%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Ashwin Iyer}
\address{Boston, MA}
\availability{Availability: July -- Aug 2026}
\contacts{(682) 239-9481 \linebreak iyer.ashw@northeastern.edu \linebreak ashwiniyer.com}

\begin{document}

	% Print the header
	\makeheader
	\vspace{-2mm}
	\begin{cvsection}{Education}
		\begin{cvsubsection}{ Boston, MA}{Northeastern University}{Expected May 2028}
		\textbf{Candidate for Bachelor of Science in Computer Science and Business Administration \hfill{GPA: 3.7}}
		\textbf{Honors/Activities:} NU Systematic Alpha
		\vspace{-2mm}
			
		\textbf{Relevant Coursework:} Discrete Structures, Introduction to Databases, Program Design \& Implementation, Business Statistics, Financial Management
		\end{cvsubsection}
	\end{cvsection}
	% Print the content
\vspace{-3mm}

\begin{cvsection}{Languages and Technologies}
	\begin{cvsubsection}{}{}{}	

\textbf{Languages:} C++, Java, Python, JavaScript, TypeScript, SQL, Kotlin
\vspace{-2mm}

\textbf{Frameworks \& Libraries:} React, Electron, Redux, TensorFlow, Keras, Pandas, NumPy
\vspace{-2mm}

\textbf{Developer Tools:} Git, IntelliJ, Eclipse, PyCharm, Xcode, PostgreSQL, Microsoft ADO
	\end{cvsubsection}
\end{cvsection}
\vspace{-2mm}

			\begin{cvsection}{Work Experience}
		\begin{cvsubsection}{Global Risk \& Analytics Co-op}{Wellington Management}{December 2025 -- June 2026}			
			\begin{itemize}
				% \item Global Risk \& Analytics Co-op at Wellington Management on the Risk \& Analytics team.
				\item Engineered advanced risk management tools in Python, utilizing proprietary \textbf{factor risk models} to compute risk metrics for equities and alternative asset classes to support quantitative research.
			\end{itemize}
		\end{cvsubsection}
\vspace{-2mm}

		\begin{cvsubsection}{Software Engineering Intern}{Zeal IT Consultants}{May 2025 -- August 2025}			
			\begin{itemize}
				\item Developed the frontend for Trinity Industries' Asset Management System using React and Next.js.
				\smallskip
				\item Increased sprint capacity for UI development by \textbf{over 10 story points per sprint}, accelerating the project timeline by 4 weeks, and increased the overall team delivery capacity by \textbf{300\%} within one release cycle.
				\smallskip
				\item Decreased page loading times by migrating from MobX to Redux in addition to implementing server-side rendering, resulting in a \textbf{94\%} decrease in page load times.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	\vspace{-2mm}

	\begin{cvsection}{Projects}
		\begin{cvsubsection}{}{}{}	
                \textbf{NU Co-op Screener | }\textit{JavaScript, NLP.js} \hfill{December 2025 -- Present} 
				\begin{itemize}
					\item Created a Chrome extension that allows users to input their resume to screen skills and graduation date against jobs within the Northeastern portal to automatically favorite relevant jobs, decreasing job search time.
					\smallskip
					\item Used NLP.js to filter out ineligibility due to graduation year and \textbf{cosine similarity} to find similarities between the user's skills and job descriptions.
				\end{itemize}
				\medskip
				\textbf{Row 2 Reach | }\textit{Electron, JavaScript} \hfill{September 2025 -- Present}
				\begin{itemize}
					\item Created a desktop application that allows users to find people's emails given their name and company using Electron and JavaScript.
					\smallskip
					\item Utilized Electron Builder and Electron Winstaller to allow for cross-platform compatibility, easy installation, and automatic updates.
				\end{itemize}
				\medskip
				\textbf{Algorithmic Options Trading | }\textit{Python, TypeScript, Pandas, NumPy} \hfill{August 2024 -- December 2024}
				\begin{itemize}
					\item Built an algorithmic trading tool that utilized the difference between \textbf{implied volatility} and realized volatility to suggest option strategies.
					\smallskip
					\item Used the \textbf{Black-Scholes model} to calculate implied volatility and compared it against historical volatility to perform a \textbf{volatility mean reversion} by buying underpriced straddles.
				\end{itemize}
				\medskip
				\textbf{PaveGuard | }\textit{React, Python, YOLO} \hfill{October 2023}
				\begin{itemize}
					\item Developed an image recognition model to categorize potholes and other road fractures, enabling a crowdsourced approach to addressing city infrastructure needs.
					\smallskip
					\item Trained a YOLO model on road fractures and hosted the backend locally. Awarded the \textbf{top prize} in the AI for All hackathon hosted at the University of Texas at Dallas.
				\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
\vspace{-2mm}
	\begin{cvsection}{Interests}
		\begin{cvsubsection}{}{}{}
			\medskip
				Hackathons, Reading, Rubik's Cube, Chess, Poker, Baseball, Blogging, Football, Working Out, Watches, Shoes
		\end{cvsubsection}
	\end{cvsection}

	
\end{document}

